### 2021-11-04 paper/pldi22/abstract.tex
Revised intro

\begin{abstract}\label{sec:abstract}
  JavaScript is a widely-used programming language in various fields. Recently,
  it has rapidly evolved with a yearly release cadence and open development
  process to adapt users' demands to the language quickly. In this fast-evolving
  nature of JavaScript, developers and even language designers often suffer from
  complex semantics in newly introduced language features and desire to
  understand them correctly.  To meet the demand, researchers have proposed
  several tools that enhance the understanding of JavaScript semantics. However,
  existing tools 1) require manual updates for new specifications or 2) do not
  provide any automatic ways to focus on specific semantics.

  To alleviate this problem, we present $\tool$, a JavaScript interactive
  specification. First, it provides step-by-step program execution automatically
  synchronized with a given version of JavaScript specification. Second, our
  tool offers two approaches to focus on target semantics: 1) reducing semantics
  with a user-defined \textit{syntactic view} and 2) providing a small-sized
  program related to a selected algorithm step with automatically inferred
  assertions. For evaluation, we experimentally demonstrate the effectiveness of
  $\tool$ with the latest ECMAScript (ES12, 2021), \inred{177} syntactic views,
  and \inred{19,839} programs. Our tool successfully reduces \inred{18.9}\%
  algorithm steps for each syntactic view on average. For each algorithm step,
  it provides \inred{2.3} lines (\inred{152.3} bytes) of a program with
  automatically inferred assertions on average.
\end{abstract}

>>>>

\begin{abstract}\label{sec:abstract}
  JavaScript is a widely-used programming language in various fields.
  Unfortunately, developers and even language designers often suffer from
  complex semantics in JavaScript and desire to \textit{understand} them
  correctly. Therefore, researchers have presented several tools for a better
  understanding of JavaScript semantics. However, existing tools 1) require
  manual updates for new specifications while JavaScript has rapidly evolved
  with various language features and 2) do not support user interactions to
  select target semantics to get additional information.

  To alleviate this problem, we present $\tool$, a JavaScript interactive
  specification. First, it provides step-by-step program execution automatically
  synchronized with a given version of JavaScript specification. Second, our
  tool supports two different types of user interactions to select target
  semantics: 1) a \textit{syntactic view selection} to reduce abstract
  algorithms using \textit{partial evaluation} and 2) an \textit{algorithm step
  selection} to get a small-sized JavaScript program related to the step using
  \textit{delta debugging} with a given set of programs. For evaluation, we
  experimentally demonstrate the effectiveness of $\tool$ with the latest
  ECMAScript (ES12, 2021), \inred{177} syntactic views, and \inred{19,839}
  programs. Our tool successfully supports step-by-step program execution in
  ES12. It reduces \inred{18.9}\% algorithm steps for each syntactic view and
  provides \inred{2.3} lines (\inred{152.3} bytes) of a program for each step on
  average.
\end{abstract}

### 2021-11-04 paper/pldi22/intro.tex
Revised intro

In the beginning, JavaScript was a scripting language designed in a ten-day
hack. However, it has become a de facto Web standard and eventually becomes one
of the dominating programming languages in various fields. For example, Node.js
introduced full-stack JavaScript by supporting server-side programming, and
JavaScript has recently begun to be used even in embedded systems and
microcontrollers for the Internet of Things (IoT). Furthermore, according to the
annual report of GitHub\footnote{\url{https://octoverse.github.com/}},
JavaScript has consistently been the most popular programming language based on
the number of contributors to GitHub projects.

Recently, JavaScript has rapidly evolved with a yearly release cadence and open
development process. In 2015, The Ecma Technical Committee 39 (TC39) decided to
annually release ECMAScript, the standard specification for JavaScript, with a
massive update in ECMAScript 2015 (ES6, 2015)~\cite{es6}. Moreover, they
published the specification as an open-source project in a GitHub repository to
quickly adapt users' demands to the language.

In this fast-evolving nature of JavaScript, the need for language design
assistants (LDAs)~\cite{lda} has grown to understand original or revised
semantics correctly in the revision process. Historically, researchers have
proposed several language design assistants, such as LISA~\cite{lisa} and
$\asfsdf$~\cite{asf-sdf, meta-env}, with semantics editors and the generators
for language-based tools, such as parsers, compilers, interpreters, and so on.
However, only small-size domain-specific languages are their targets due to
their low expressive power. On the other hand, there are several attempts to
develop language design assistants for JavaScript in the academy and industry.
For example, in the academy, \citet{jsexplain} presented JSExplain, a JavaScript
reference interpreter written in OCaml that closely follows ECMAScript and
produces execution traces for debugging both ECMAScript and a given program. In
the industry, Mozilla and several contributors introduced JavaScript
interpreters written in pure JavaScript, such as Narcissus~\cite{narcissus} and
engine262~\cite{engine262}, to aid the development of new features in
JavaScript.

However, existing language design assistants for JavaScript have two
limitations: \textit{manual updates} and \textit{lack of connection with
conformance tests}. First, all existing assistants are developed manually; thus,
developers should manually update them for each frequent evolution of
ECMAScript. This manual approach is a tedious, labor-intensive, and even
error-prone process. Moreover, they lack information about the relationship
between specific semantics with conformance tests. When a language designer
desires to understand specific language semantics, one possible approach is to
learn them from related conformance tests. Fortunately, TC39 provides Test262,
an official conformance test suite for the latest version of ECMAScript.
However, existing assistants do not utilize them to give a better comprehension
of language semantics.

In this paper, we present $\tool$, a \textit{live} language design assistant for
JavaScript, which automatically synchronizes with a given language specification
and shows related conformance tests in the revision process. To synchronize our
tool with ECMAScript, we utilize another tool $\jiset$~\cite{jiset}, which
automatically extracts a mechanized specification from a given version of
ECMAScript. Note that a specification is mechanized if and only if it is both
executable and formalized.
\todo

>>>>

In the beginning, JavaScript was a scripting language designed in a ten-day
hack. However, it has become a de facto Web standard and eventually becomes one
of the dominating programming languages in various fields. For example,
Node.js\footnote{https://nodejs.org/} introduced full-stack JavaScript by
supporting server-side programming, and JavaScript has recently begun to be used
even in embedded systems and microcontrollers for the Internet of
Things\footnote{https://www.espruino.com/}. Furthermore, according to the annual
report of GitHub\footnote{\url{https://octoverse.github.com/}}, JavaScript has
consistently been the most popular programming language based on the number of
contributors to GitHub projects.

Unfortunately, developers and even language designers often suffer from complex
semantics in new language features and desire to understand them correctly.
ECMAScript is the standard specification for JavaScript maintained by Ecma
Technical Committee 39 (TC39). It describes the language semantics in abstract
algorithms consisting of English sentences. However, it is infeasible to know
all the detailed complex semantics by reading the specification even to language
designers. For example, consider a JavaScript logical nullish assignment
\jscode{x ??= y} newly introduced in the latest ECMAScript (ES12,
2021)~\cite{es12}. Its basic semantics is to assign \jscode{y} to \jscode{x}
only if \jscode{x} is nullish (\jscode{undefined} or \jscode{null}). Therefore,
it seems to have exactly same semantics with an assignment \jscode{x = x ?? y}
with a nullish coalescing operator \jscode{??}.  However, it is not true because
of the short-circuiting for assignments:
\begin{lstlisting}[style=JS]
       const x = 0;  x ??= 1;    // x === 0
       const y = 0;  y = y ?? 1; // TypeError
\end{lstlisting}
and the named evaluation for anonymous functions:
\begin{lstlisting}[style=JS]
   let f;  f ??= () => {};      // f.name === "f"
   let g;  g = g ?? (() => {}); // g.name === ""
\end{lstlisting}
Such misunderstanding of complex semantics in various language features causes
the wrong implementation of JavaScript applications or even JavaScript engines.

Thus, researchers have presented several tools for a better understanding of
JavaScript semantics. For example, JSExplain~\cite{jsexplain} is a reference
interpreter that provides step-by-step execution of a given JavaScript program
by closely following the English sentences of the specification. Several
JavaScript language designers accept the concept of reference interpreters and
implement Narcissus~\cite{narcissus} and engine262~\cite{engine262} to use in
the language design process. On the other hand, TC39 feels the need for type
information in ECMAScript to enhance its readability and has started internal
discussions on manual type annotations for each abstract
algorithm\footnote{https://github.com/tc39/ecmarkup/issues/173}. To meet the
demand of type information, \citet{jstar} presents a tool named $\jstar$ to
perform a type analysis for a given ECMAScript. Besides, they detect
type-related specification bugs in ES12 using the type analysis result. Finally,
$\jest$~\cite{jest} is another tool that synthesizes JavaScript conformance
tests from a given ECMAScript. Thus, it allows users to understand language
semantics using test programs instead of English sentences in the specification.

However, existing tools have two limitations: 1) manual update for evolving
language specification and 2) no user interactions to select target semantics.
Among existing tools, JavaScript reference interpreters require manual updates
when ECMAScript evolves. Until 2015, it was not a critical problem because
ECMAScript had rarely evolved. However, TC39 decided to annually release the
specification with a massive update in ECMAScript 6 (ES6, 2015)~\cite{es6} in
2015. Moreover, they published the specification as an open-source project in a
GitHub repository to quickly adapt users' demands to the language. For example,
JSExplain also requires manual updates for new specifications. Thus, it still
supports only ECMAScript 5.1 (ES5.1, 2011)~\cite{es5}, while already seven more
versions from ES6 to ES12 have been released. Another limitation is that
existing tools do not support user interactions to select target semantics to
get additional information. For example, $\jstar$ and $\jest$ do not interact
with users to give more information helpful for semantics understanding.
Instead, they only extract type information and conformance tests for a given
ECMAScript. On the other hand, while JSExplain supports step-by-step execution
as user interaction with several debugger-like features, it can deal with only
the execution trace of a single JavaScript program.

In this paper, we present $\tool$, a \textbf{J}ava\textbf{S}cript
\textbf{I}nteractive \textbf{S}pecification. It is the first reference
interpreter automatically synchronized with a given ECMAScript supporting
step-by-step program execution. Fortunately, \citet{jiset} presents a tool named
$\jiset$ that extracts a mechanized specification from a given specification.
The extracted mechanized specification is written in a specification language
$\ires$ and executable with a JavaScript program. Thus, we implement our tool
using $\jiset$ and design debugger-like features: stepping controls, state
visualization, and breakpoints with algorithm names or JavaScript program
points. Moreover, our tool supports two different types of user interactions to
select target semantics: \textit{syntactic view selection} and \textit{algorithm
step selection}. First, we introduce a way to reduce abstract algorithms using a
partial evaluation~\cite{peval, peval-survey, trans-ai} with a \textit{syntactic
view}. A syntactic view is a JavaScript Abstract Syntax Tree (AST) defined with
abstracted nodes. We formally define a partial evaluation with syntactic views
and prove its semantics preservation under the given syntactic view. Second, we
also present a way to extract a small-sized program for each algorithm step
using delta debugging~\cite{delta-debugging} with a given set of programs. For
the f first step, we execute each program using $\tool$ to compute semantics
coverage in ECMAScript and filter out unnecessary programs. Then, we perform
delta debugging for each program to reduce program sizes without loss of
semantics coverage.

Our contributions are as follows:
\begin{itemize}
  \item We present $\tool$, a JavaScript interactive specification. It is the
    first reference interpreter automatically synchronized with a given
    ECMAScript supporting step-by-step program execution.

  \item We introduce two different types of user interactions to select target
    semantics and implement them in $\tool$: 1) a \textit{syntactic view
    selection} to reduce abstract algorithms using \textit{partial evaluation}
    and 2) an \textit{algorithm step selection} to extract a small-sized
    JavaScript program related to the selected step using \textit{delta
    debugging} with a given set of programs.

  \item We evaluate $\tool$ with the latest ECMAScript, ES12, and experimentally
    show the effectiveness of two different target semantics selections with
    \inred{177} syntactic views and \inred{19,839} programs. Our tool
    successfully supports step-by-step program execution in ES12. It reduces
    \inred{18.9}\% algorithm steps for each syntactic view and provides
    \inred{2.3} lines (\inred{152.3} bytes) of a program for each step on
    average.
\end{itemize}
